ABC

### 2024-11-10 tab.qmd
more

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false
ManifoldDestiny::wasmconload()
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
apps <- apsnn
adat <- apps[[1]]
amet <- apps[[2]]
cogr <- Countinggraphs(apps[[1]])
selo <- seloutput(selreport(apps))
#options(digits = 2)                                                                                               
```

>>>>

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false
ManifoldDestiny::wasmconload()
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
apps <- apsnn
#apps <- aprnn
#apps <- aprhn
#apps <- apron
#apps <- apn1n
#apps <- apn2n
#apps <- apn3r
#apps <- apn4n
#apps <- apn5an
#apps <- apn5bn
adat <- apps[[1]]
amet <- apps[[2]]
cogr <- Countinggraphs(apps[[1]])
selo <- seloutput(selreport(apps))
#options(digits = 2)                                                                                               
```

### 2024-11-10 tabset.qmd
fixed
more

::: {.callout-caution collapse="true"}
## {{< var tabh.h2 >}}
```{r}
#| echo: false
#| output: false
apps <- aprnn
```
{{< include tab.qmd >}}
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h3 >}}
```{r}
#| echo: false
#| output: false
apps <- aprnn
```
{{< include tab.qmd >}}
:::
::: {.callout-caution collapse="true"}
## {{< var sec6.2.1 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tab.qmd >}}
:::
::: {.callout-caution collapse="true"}
## {{< var sec6.2.2 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tab.qmd >}}
:::
```{r}
knitr::knit_exit()
```
::: {.callout-caution collapse="true"}
## {{< var sec6.2.3 >}}
```{r}
#| echo: false
#| output: false
apps <- appn3
```
{{< include tab.qmd >}}
:::

>>>>

::: {.callout-caution collapse="true"}
## {{< var tabh.h2 >}}
```{r}
#| echo: false
#| output: false
apps <- aprhn
```
{{< include tab.qmd >}}
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h3 >}}
```{r}
#| echo: false
#| output: false
apps <- aprhn
```
{{< include tab.qmd >}}
:::
::: {.callout-caution collapse="true"}
## {{< var sec6.2.1 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tab.qmd >}}
:::
::: {.callout-caution collapse="true"}
## {{< var sec6.2.2 >}}
```{r}
#| echo: false
#| output: false
apps <- apn1n
```
{{< include tab.qmd >}}
:::
```{r}
knitr::knit_exit()
```
::: {.callout-caution collapse="true"}
## {{< var sec6.2.3 >}}
```{r}
#| echo: false
#| output: false
apps <- appn3
```
{{< include tab.qmd >}}
:::
